
---
title: "Network Meta-Analysis Using Summary Log(HR) Data"
author: "Yolande Tra"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
    highlight: tango
    theme: readable
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This R Markdown demonstrates how to perform a network meta-analysis using study-level summary statistics (log hazard ratios and standard errors).

## Load Required Libraries

```{r libraries}
library(netmeta)
```

## Read Summary Data

```{r read-summary}
nma_data <- read.csv("C:/Users/trani/OneDrive/heor-survival-nma/data/nma_summary_loghr_data.csv")
print(nma_data)
```

## Perform Network Meta-Analysis

```{r netmeta-analysis}
net <- netmeta(TE = nma_data$logHR,
               seTE = nma_data$SE,
               treat1 = nma_data$treat1,
               treat2 = nma_data$treat2,
               studlab = nma_data$study_id,
               sm = "HR",
               common = TRUE,
               random = TRUE)
summary(net)
```

## Plot the Treatment Network and Forest Plot

```{r plot-network}
netgraph(net, thickness = "se.random", multiarm = TRUE)
```

```{r forest-plot}
forest(net, ref = "A")
```

## Conclusion

This workflow demonstrates a simplified example of survival-based network meta-analysis using log(HR) and standard errors from Cox models across studies.
